Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-04 src/paper.tex
update

\subsection{Encoding}
We use pretrained SSL model WavLM Large \cite{wavlm} to 
encode the speech into continuous representations. We use the output from 6 hidden 
layers 1, 3, 7, 12, 18, 23. Given a speech signal \(s \in R^{T'} \), the output 
of WavLM will be a tensor \(\bm{r}\) of shape \(n \times T \times E\) where 
\(n\) specifies the number 
of output layers (6 in this case), and  \(T\) is the time 
dimension and \(E\) stands for the 
embedding dimension, specifically 1024 in WavLM Large. The Kmeans tokenizer uses \(n\) numbers of  Kmeans model 
separately on each output layer. Each model uses the same clustering number denoted by \(K\).
After tokenization, the continuous embedding \(\bm{r}\) will be transformed to a tensor \(\bm{d}\) of shape \(n \times T\) where each value \(\bm{d}_{(n_i,t)} \in (0, K-1), n_i \in (0,n), t \in 
(0, T)\). We choose \(K\) to be 1000 in our experiments.

The encoding strategy on the mixed speech plays a pivotal role in the model performance. 
We follow the 
aforementioned procedure for reference speech to get tensor \(\bm{d_r}\) of shape . But for the mixed speech.

>>>>

\subsection{Encoding}
We use pretrained SSL model WavLM Large \cite{wavlm} to 
encode the speech into continuous representations. We use the output from 6 hidden 
layers 1, 3, 7, 12, 18, 23. Given a speech signal \(s \in R^{T'} \), the output 
of WavLM will be a tensor \(\bm{r}\) of shape \(n \times T \times E\) where 
\(n\) specifies the number 
of output layers (6 in this case), and  \(T\) is the time 
dimension and \(E\) stands for the 
embedding dimension, specifically 1024 in WavLM Large. The Kmeans tokenizer uses \(n\) numbers of  Kmeans model 
separately on each output layer. Each model uses the same clustering number denoted by \(K\).
After tokenization, the continuous embedding \(\bm{r}\) will be transformed to a tensor \(\bm{d}\) of shape \(n \times T\) where each value \(\bm{d}_{(n_i,t)} \in (0, K-1), n_i \in (0,n), t \in 
(0, T)\). We choose \(K\) to be 1000 in our experiments. For reference speech and mixed speech, we 
use the same Kmeans model and the same layer output of WavLM.

The encoding strategy on the mixed speech plays a pivotal role in the model performance. 
We follow the 
aforementioned procedure for 
reference speech to get tensor \(\bm{d_r}\) of shape \(n \times T_r\). But for the mixed 
speech, instead of directly following the procedure, we first concatenate it with 
the reference speech to get \(s' = [s_r, s_m, s_r] \in R^{()}\)
